Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-16 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

\begin{thm}\cite{GilboaSchmeidler1994,Grabisch2016}For every classical
interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
and any random variable~$X:\Omega\rightarrow\mathbb{R}$, $\bar{\mu}$
is convex if and only if

\begin{equation}
\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\textrm{ .}
\end{equation}
\end{thm}

@@

Consider a quantum IVPM~$\bar{\mu}$ such that $l:\events\rightarrow\left[0,1\right]$
and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
Given the same observable with an extra condition~$x_{1}\le x_{2}\le\ldots\le x_{N-1}\le x_{N}$,
we can combine equation~(\ref{eq:interval-expectation}) and (\ref{eq:quantum-expectation})
to define the expectation value of $\mathbf{O}$ with respect to $\bar{\mu}$
as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N}\lambda_{i}\left[l\left(\sum_{j\ge i}P_{j}\right)-l\left(\sum_{j\ge i+1}P_{j}\right),r\left(\sum_{j\ge i}P_{j}\right)-r\left(\sum_{j\ge i+1}P_{j}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{equation}

>>>>

\begin{thm}\cite{GilboaSchmeidler1994,Grabisch2016}For every classical
IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and any random variable~$X:\Omega\rightarrow\mathbb{R}$,
$\bar{\mu}$ is convex if and only if 
\begin{equation}
\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\textrm{ .}
\end{equation}
\end{thm}

@@

Consider a quantum IVPM~$\bar{\mu}$ such that $l:\events\rightarrow\left[0,1\right]$
and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
Given the same observable with an extra condition~$x_{1}\le x_{2}\le\ldots\le x_{N-1}\le x_{N}$,
we can combine equation~(\ref{eq:interval-expectation}) and (\ref{eq:quantum-expectation})
to define the expectation value of $\mathbf{O}$ with respect to $\bar{\mu}$
as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N}\lambda_{i}\left[l\left(\sum_{j\ge i}P_{j}\right)-l\left(\sum_{j\ge i+1}P_{j}\right),r\left(\sum_{j\ge i}P_{j}\right)-r\left(\sum_{j\ge i+1}P_{j}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{equation}
Let $\events'$ denote the minimal commuting sub-event space containing
$\left\{ P_{i}\right\} _{i=1}^{N}$. Then, we have the corresponding
theorem.

\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
and any observable~$\mathbf{O}$, if $\bar{\mu}$ is convex, then
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\mathrm{core}\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\mathrm{core}\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
\end{equation}
Conversely, if equation~(\ref{eq:quantum-interval-expectation-core})
holds for every observable, then $\bar{\mu}$ is convex.\end{thm}
